Selective electroporation of the viral envelope

### 2021-04-06 documents/pure_electroporation.tex
kotnik

Viruses have extraordinary mechanical properties\footnote{Why is this? What selection pressures drive this selected pressure?}, so it seems reasonable that their dielectric properties may differ substantially from that of other structures. In the case of bacteriophages, the genome is packaged so tightly that the core is best considered an amorphous, glass-like material. ssRNA viruses like coronaviridae are perhaps somewhat less . On the other hand, the human "structome"

>>>>

Viruses have extraordinary mechanical properties\footnote{Why is this? What selection pressures drive the selected pressure?}, so it seems reasonable that their dielectric properties could differ substantially from that of other structures. In the case of bacteriophages, the genome is packaged so tightly that the core is best considered an amorphous, glass-like material. ssRNA viruses like coronaviridae are perhaps somewhat less . On the other hand, the human "structome" also contains countless lipid vesicles that might plausibly

The most obvious difference is scale. Viruses are minute. The classic Schwan equation implies that the transmembrane voltage
